\documentclass[letter]{amsart}
\usepackage[pdftex]{geometry}
\usepackage[utf8]{inputenc}

\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{courier}
\usepackage{fancyhdr}

\lstset{language=C++}
\lstset{columns=fullflexible}
\lstset{basicstyle=\scriptsize\ttfamily}
\lstset{showspaces=false}

\geometry{landscape}
\setlength{\topmargin}{-0.25in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\columnsep}{1in}
\setlength{\columnseprule}{0.2pt}
\textwidth 9.5in

\pagestyle{fancy}
\lhead{ Universidad de la Habana: UH-Top }
\chead{}
\rhead{\thepage}
\lfoot{}
\cfoot{}
\rfoot{}

\newcommand{\includecpp}[3]{
  \begin{multicols}{2}
    [\subsection{#1}\ ]
    \lstinputlisting[language=c++]{#2/#3}
  \end{multicols}
}

\newcommand{\includejava}[3]{
  \begin{multicols}{2}
    [\subsection{#1}\ ]
    \lstinputlisting[language=Java]{#2/#3}
  \end{multicols}
}

\newcommand{\stirlingfirst}[2]{\genfrac{[}{]}{0pt}{}{#1}{#2}}
\newcommand{\stirlingsecond}[2]{\genfrac{\{}{\}}{0pt}{}{#1}{#2}}
\newcommand{\norm}[1]{\lVert#1\rVert}

\begin{document}
  \thispagestyle{fancy}
  \begin{center}
    \Huge\textsc{Team Reference \\ Universidad de la Habana : UH-Top }
  \end{center}
  
  \begin{center}
    \textbf{ ICPC Caribbean Finals 2024 }\\
    \textbf{Team Members:} Ariel Gonzales Gomez , Jorge Pichardo Cabrera, Leonardo Artiles Montero\\
    \textbf{Developed by:} Alfredo Somoza
  \end{center}  

  \begin{multicols}{2}
    \tableofcontents
  \end{multicols}

  

  \enlargethispage*{\baselineskip}
  \pagebreak

  \section{ Extended team reference }
     \include {.cph}{./extended team reference}{.cph.}
     \include {Data Structures}{./extended team reference}{data_structures.}
     \include {Dynamic Programming}{./extended team reference}{dynamic_programming.}
     \include {Geometry}{./extended team reference}{geometry.}
     \include {Graph}{./extended team reference}{graph.}
     \include {Helpers}{./extended team reference}{helpers.}
     \include {Java}{./extended team reference}{java.}
     \include {Math}{./extended team reference}{math.}
     \include {Misc}{./extended team reference}{misc.}
     \include {Number Theory}{./extended team reference}{number_theory.}
     \includetex {Reference}{./extended team reference}{reference.tex}
     \includepy {Render}{./extended team reference}{render.py}
     \include {String}{./extended team reference}{string.}
     \includetex {Template}{./extended team reference}{template.tex}
    
  

  \enlargethispage*{\baselineskip}
  \pagebreak

  \section{ Team-reference-2023 }
     \include {Data Structures}{./team-reference-2023}{data_structures.}
     \include {Geometry}{./team-reference-2023}{geometry.}
     \include {Graph}{./team-reference-2023}{graph.}
     \include {Math}{./team-reference-2023}{math.}
     \include {Number Theory}{./team-reference-2023}{number_theory.}
     \includemd {Readme}{./team-reference-2023}{README.md}
     \includetex {Reference}{./team-reference-2023}{reference.tex}
     \includepy {Render}{./team-reference-2023}{render.py}
     \include {String}{./team-reference-2023}{string.}
     \includetex {Template}{./team-reference-2023}{template.tex}
     \include {Useful}{./team-reference-2023}{useful.}
    
  
\end{document}